Effects of the body force on the evacuation dynamics

### 2019-12-26 paper.tex
Update paper.tex

The complex behavior of pedestrians feature either his (her) feelings and 
the environmental conditions. The former is expressed, for example, by his 
(her) moving ``attitude'' (say, self-assuredness). The latter brings out the 
observed separation between pedestrians. Also, the ``contacts'' between 
individuals address some kind of ``unwanted'' slowing down. All these 
observed patterns are commonly quantified in the literature into a a set of 
characteristic  parameters. The experimental meaning of these parameters is as 
follows.

@@

\hline
\end{tabular}
\caption{The experimental data for the pedestrian parameters, as explained in 
Section~\ref{experimental}. The magnitude $v$ means de pedestrian velocity 
(m/s). The magnitude $x$ means the compression length (m). The upper row for 
Ref.~\cite{song_2019} corresponds data acquired in winter and the lower row to 
datas acquiquired in summer. The asterisk ($^*$) corresponds to reasonable 
estimates. }
\label{table_data}
\end{table}

>>>>

The complex behavior of pedestrians feature either his (her) feelings and 
the environmental conditions. The former is expressed, for example, by his 
(her) moving ``attitude'' (say, self-assuredness). The latter brings out the 
observed separation between pedestrians. Also, the ``contacts'' between 
individuals address some kind of ``unwanted'' slowing down. All these 
observed patterns are commonly quantified in the literature into a set of 
characteristic  parameters. The experimental meaning of these parameters is as 
follows.

@@

\hline
\end{tabular}
\caption{The experimental data for the pedestrian parameters, as explained in 
Section~\ref{experimental}. The magnitude $v$ means de pedestrian velocity 
(m/s). The magnitude $x$ means the compression length (m). The upper row for 
Ref.~\cite{song_2019} corresponds data acquired in winter and the lower row to 
datas acquiquired in summer. The asterisk ($^*$) corresponds to reasonable 
estimates from the authors. }
\label{table_data}
\end{table}
